rowing: analysis of sculls in the 2016 Olympics

### 2021-02-01 inst/rowing.Rmd
correct removal of dominating or dominated rowers

We may then analyse this:

@@

This is a much more manageable dataset, much easier to study and less
cluttered, as competitors with zero estimated strength are not
present. *However, it is incorrect as `drysdale` does not appear.
Something is wrong.*

```{r minimalmaxp,cache=TRUE}
(rowing_minimal_maxp <- maxp(rowing_minimal))
```

```{r maxpcalcminimal,fig.cap="Minimal dataset, maximum likelihood estimate of strength"}
dotchart(rowing_minimal_maxp)
```

>>>>

(also, we have removed `drysdale`, as he won everything and his ML
strength would be 1).  We may then analyse this:

@@

This is a much more manageable dataset, much easier to study and less
cluttered, as competitors with zero estimated strength are not
present.

```{r minimalmaxp,cache=TRUE}
rowing_minimal_maxp <- maxp(rowing_minimal)
rowing_minimal_maxp
```

```{r maxpcalcminimal,fig.cap="Minimal dataset, maximum likelihood estimate of strength"}
dotchart(rowing_minimal_maxp)
dotchart(log10(rowing_minimal_maxp))
```
